# Results

```{r}
# Import All Necessary Libraries
library(tidyverse)
library(patchwork)
library(repr)
library(ggnewscale)
library(RColorBrewer)
library(Lock5withR)
library(naniar)
library(ggplot2)
library(ggplot2)
library(gganimate)


# Import Helper Libraries
source("R_Scripts/plot_missing.R")
source("R_Scripts/readJar.R")
source("R_Scripts/readGVA.R")
```

## Most frequent places for hatecrime

```{r cleveland}
df <- read_csv("data/processed/ucr/annual_hc_count_by_place.csv",show_col_types = FALSE)
df$min <- apply(df[2:11], MARGIN =  1, FUN = min, na.rm = T)
df$max <- apply(df[2:11], MARGIN =  1, FUN = max, na.rm = T)
#df$Total <- rowSums(df[ , c(2,3,4,5,6,7,8,9,10,11)], na.rm=TRUE)
filter(df, Place != "Other/unknown") %>% mutate(Place = fct_reorder(Place, max, .desc = FALSE)) %>% ggplot() +  geom_point(aes(min, Place, color = "Min")) +
  geom_point(aes(max, Place, color = "Max")) +
  theme(plot.title = element_text(hjust = 0.5), axis.line = element_line(colour = "black"))+
  ggtitle("Maximum and Minimum Incidents w.r.t. Location")+
  xlab('Incidents') +
  ylab('Location')
```

We use a Cleaveland dot plot for finding out the places where a hate crime happens more frequently. This can helps us understand if it's just the unavailablity of sufficient survilleance or any other motivation that makes these location more prone to such crimes. Thus we can take measures to strengthen the public security in these places.

We can observe that the top 4 spots for hate motivated crimes are:

- Residental Areas
- Roads
- Schools
- Parking Lots

The number of crimes observed in these areas over the last decade far outweigh the incidents observed in other locations such has hotels or grocery store.

Residential areas being the most frequent spots can let us to the assumption that a large portion of these crimes are committed by individuals due to thier bias towards particular people rather than a group perhaps due to the ease of attacking small number rather than going for a large riot.

The presence of schools/colleges corroborates our concerns of the rise of intolerance in the youth especially the teenagers who tend to be easily carried away by agendas propagated on social media platforms like Twitter, Facebook or Instagram.

> Recent Instance:
>
> - [2021 Michigan School Shooting](https://apnews.com/article/oxford-high-school-shooting-shootings-michigan-school-shootings-9bc485fb234a873d0d1fcc99bab6379f)

The existence of large number of such crimes in parking spots/garage might suggest that there is a lack of sufficient security or survelliance for these areas usually spread across several acres or on the secluded portions of a building/store might need some reinforcement.

> Recent Instance:
>
> - [Hayward Parking Lot Shooting](https://www.nbcbayarea.com/news/local/east-bay/shooting-in-hayward-parking-lot/2753592/)

## Rate of Crimes over the years

```{r sumtype}
df <- read_csv("data/processed/ucr/FBI_UCR_TABLE2_Incidents.csv",show_col_types = FALSE)
df2 <- df[c(1,2, 8, 16), ]
df2 %>%
  pivot_longer(., -Crime, values_to = "Incidents", names_to = "Year") %>%
  ggplot(., aes(x=Year, y=Incidents, group=Crime)) +
  geom_line(aes(color=Crime)) + geom_point(size =0.5) +
  geom_vline(xintercept = 8, size =0.5, color = 'brown3')+
  geom_vline(xintercept = 4, size =0.5, color = 'deepskyblue4')+
  annotate("text", x = 2.8, y = 7000, label = "Obama Re-elected", size =3)+
  annotate("text", x = 9, y = 7000, label = "Trump elected", size =3)+
  ggtitle("Incidents vs Years (Aggregated types)")
```

We can observe from the above time series data, that the total number of hate crimes were on a decline till 2013 (i.e President Obama's second run for office). However it started rising again significantly from 2016 especially leading to a sharp increase (much more than what was observed in the previous decade) by 2017. This was the time during which Donald Trump Jr. was running for the office of US President. This insight might suggest a correlation between the change of political behaviour of the administration and the number of occurances of hate crimes.

> Recent Instance:
>
> [NYT Article on the rise of hate crime violene during Trump Administration](https://www.nytimes.com/2019/11/12/us/hate-crimes-fbi-report.html)

Another striking observation is the sudden drop in crime against property (i.e vandalism) during the Trump Administration.

```{r type}
df <- read_csv("data/processed/ucr/FBI_UCR_TABLE2_Incidents.csv",show_col_types = FALSE)
df2 <- df[-c(1,2, 8,15, 16), ]
df2 %>%
  pivot_longer(., -Crime, values_to = "Incidents", names_to = "Year") %>%
  ggplot(., aes(x=Year, y=Incidents, group=Crime)) +
  geom_line(aes(color=Crime)) + geom_point(size =0.5) +
  geom_vline(xintercept = 8, size =0.5, color = 'brown3')+
  geom_vline(xintercept = 4, size =0.5, color = 'deepskyblue4')+
  annotate("text", x = 2.8, y = 3000, label = "Obama Re-elected", size =3)+
  annotate("text", x = 9, y = 3000, label = "Trump elected", size =3)+
  ggtitle("Incidents vs Years (by Types of Crime)")
```

In the above time series plot of the rates of different types of crimes over the last decade,we can see that instaces of Simple Status have remained the almost the same showing some evidence for an inherent presence of bias to harm others based on an identity within a portion of the population. This can be looked upon as a social issue that needs large scale reformation of how people percieve others in general and changes in education might help to mitigate it.

Furthermore, we can see that there is a sharp rise in robbery motivated by some kind of bias after 2018 (during Trump Administration).

```{r age}
df <- read_csv("data/processed/ucr/annual_offenders_by_age.csv",show_col_types = FALSE)
df2 <- subset(df,select = -c(2,3,4))
df2 <-pivot_longer(df2, -`Age Category`, values_to = "Incidents", names_to = "Year")

ggplot(df2, aes(fill=`Age Category`, y=Incidents, x=Year)) +
    geom_bar(position="dodge", stat="identity")+
    ggtitle("Incidents through Years w.r.t Age Category")
```

```{r amfm}
df <- read_csv("data/processed/ucr/FBI_UCR_TABLE1.csv",show_col_types = FALSE)
df2 <- filter(df, `Bias motivation` %in% c("Anti-Male","Anti-Female"))

#df2 <- subset(df,select = -c(2,3,4))
#df2 <-pivot_longer(df2, -`Age Category`, values_to = "Incidents", names_to = "Year")
#df2
ggplot(df2, aes(x = Year, fill = `Bias motivation`,
                 y = ifelse(test = `Bias motivation` == "Anti-Male",
                           yes = -Incidents, no = Incidents))) +
  geom_bar(stat = "identity", width = 0.5) +
 scale_y_continuous(labels = abs, limits = max(df2$Incidents) * c(-1,1)) +
  coord_flip()+ylab("Anti-Male v Anti Female") +xlab("Year") +
   scale_x_continuous(breaks = c(2013, 2014,2015,2016,2017,2018,2019))+
   ggtitle("Anti-Male vs Anti-Female Incidents through Years")
```

```{r grouped}
df <- read_csv("data/processed/ucr/FBI_UCR_TABLE1.csv",show_col_types = FALSE)
df$`Bias motivation`[df$`Bias motivation`=="Anti-Black or African American"]<-"Anti-Black"
df$`Bias motivation`[df$`Bias motivation`=="Anti-American Indian or Alaska Native"]<-"Anti-American Indian/Alaskan Native"
df$`Bias motivation`[df$`Bias motivation`=="Anti-Asian/Pacific Islander"]<-"Anti-Asian"


df2 <- filter(df, `Bias motivation` %in% c("Anti-White","Anti-Black","Anti-Black or African American","Anti-American Indian/Alaskan Native","Anti-Asian","Anti-Multiple Races, Group"))

#
#df2 <- subset(df2,select = -c(3))
#df2 <-pivot_wider(df2, values_from = "Incidents", names_from = "Year")

ggplot(df2, aes(fill=`Bias motivation`, y=Incidents, x=Year)) +
    geom_bar(position="dodge", stat="identity")+
     scale_x_continuous(breaks = c(2010,2011,2012,2013, 2014,2015,2016,2017,2018,2019))+
  ggtitle("Incidents through years w.r.t Race-Bias")

```

### Adding my Plots (Vijay)

JAR BoxPlot

```{r, fig.width=15}
source("R_Scripts/JAR-BoxPlots-Race.R")

JarBoxPlots_RacePLot()

```

```{r, fig.width=15,}
source("R_Scripts/JAR-BoxPlots.R")
JarBoxPlots()
```

```{r, fig.width=10}
source("R_Scripts/JAR-HeatMap-Gender.R")
JarHeatMap_GenderPlot()
```

```{r, fig.width=10}
source("R_Scripts/JAR-HeatMap-Race.R")
Jar_Heatmap_plot()
```

```{r,fig.width=9}
source("R_Scripts/JAR-RadarGraphs-Race.R")
JarRadarRace()
```

```{r,fig.width=9}
source("R_Scripts/JAR-RadarGraphs.R")
JarGenderRadar()
```

```{r}
source("R_Scripts/GVA-Animation.R")
GVA_Animation()

```

```{r}
source("R_Scripts/GVA-ParallelPlot.R")
GVA_ParallelPlot()
```

```{r}
source("R_Scripts/US-StateMapPlot.R")
GunViolenceStateMap()
```

```{r}
source("R_Scripts/Table8Script.R")
HCtable8_plot()
```

```{r}
source("R_Scripts/Table10-A.R")
HCtable10_HeatMap()
```

```{r}
source("R_Scripts/Table10.R")
HCtable10_plot()
```
